Differential Expression - HBCC - DLPFC - Dx - Sex

### 2020-07-31 individual-cohorts/HBCC_DLPFC_DE.Rmd
remove random_effects from model - not relevant

# Set covariates to adjust for from model selection
adjust.covars <- c("Dx_Sex", "ageOfDeath", "RIN", "IntronicRate", "IntragenicRate", "IntergenicRate")
random.effect <- c("Reported_Gender")
```

@@

col_type <- dplyr::select(COVARIATES, c(adjust.covars, random_effect)) %>%
  dplyr::summarise_all(class) %>% 
  tidyr::gather(variable, class)

@@

# Post adjusted formula
formula <- glue::glue("~ ", glue::glue_collapse(adjust.covars, sep = " + "), " + ", glue::glue_collapse(glue::glue("(1|{random_effect})"), sep = " + "))

@@

### Differential expression analysis (SCZ - Control - Other)
Genes that are differentially expressed at an FDR <= 0.05 are:
```{r set-formula}
formula <- glue::glue("~ 0 + ", glue::glue_collapse(adjust.covars, sep = " + "), " + ", glue::glue_collapse(glue::glue("(1|{random_effect})"), sep = " + "))    
```

>>>>

# Set covariates to adjust for from model selection
adjust.covars <- c("Dx_Sex", "ageOfDeath", "RIN", "IntronicRate", "IntragenicRate", "IntergenicRate")
```

@@

col_type <- dplyr::select(COVARIATES, c(adjust.covars)) %>%
  dplyr::summarise_all(class) %>% 
  tidyr::gather(variable, class)

@@

# Post adjusted formula
formula <- glue::glue("~ ", glue::glue_collapse(adjust.covars, sep = " + "))

@@

### Differential expression analysis (SCZ - Control - Other)
Genes that are differentially expressed at an FDR <= 0.05 are:
```{r set-formula}
formula <- glue::glue("~ 0 + ", glue::glue_collapse(adjust.covars, sep = " + "))    
```
